Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

\begin{abstract}
We address the dynamic properties of typical social networks, in which people
are considered as vertices while relations are considered as edges. We suppose
the evolution of a social network overtime includes new
connections between existing or newly created nodes, and also assume the graph
will evolve as a typical social network. We study the activity and centrality
metrics for nodes in such graphs by regulating a series of reasonable
properties the metrics should satisfy. We then formally define our metrics and
give their mathematical analysis. We have developed a practical based framework
to maintain the evolving large-scale network and the algorithm to compute our
metrics including historical queries in preferable time and space consumption.
Finally, we use a simple model to generate evolving data from existing social
network data and compare our metrics to static metrics. The results could imply
that dynamic centrality is more capable in spotting hot social events.\\[1.5em]

\noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
centrality, online algorithm.
\end{abstract}
% \tableofcontents
\newpage

>>>>

\begin{abstract}
This article addresses the dynamic properties of typical social networks. By
supposing that the evolution over time only includes creating new edges but no
deletion, we studies the activity and centrality metrics for nodes in
such graphs by regulating a series of reasonable properties the metrics should
satisfy. Then formal definitions are given to our metrics and
their mathematical analysis are put. We have developed a practice based framework
to maintain the evolving large-scale network and an algorithm to compute our
metrics including historical queries in acceptable time and space consumption.
Finally, we use a simple model to generate evolving graph from existing social
network data and compare our metric to the static one. The results could imply
that dynamic centrality is more capable in spotting hot social events.

\smallskip
\noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
centrality, online algorithm.
\end{abstract}
% \tableofcontents
\newpage
